An Embedding Framework for Consistent Polyhedral Surrogates

### 2019-05-23 neurips-19/poly-embed.tex
topk and minor

We augment this literature by studying a particularly natural approach for finding convex surrogates, wherein one ``embeds'' a discrete loss.
Specifically, we say a convex surrogate $L$ embeds a discrete loss $\ell$ if there is an injective embedding from the discrete reports (predictions) to a vector space such that (i) the original loss values are recovered, and (ii) a report is $\ell$-optimal if and only if the embedded report is $L$-optimal.
If this embedding can be extended to a calibrated link function, which maps approximately $L$-optimal reports to $\ell$-optimal reports, consistency follows~\cite{agarwal2015consistent}.
Common examples which follow this general construction include hinge loss as a surrogate for 0-1 loss and the abstain surrogate mentioned above. \jessiet{Really 0-2 loss, but that seems like an unimportant nuance.}

@@

\begin{proof}[Sketch]
  \emph{Well-defined:}
  For the initial construction above, we argued that if some collection such as $U,U',U''$ overlap at a $u$, then their report sets $R_U, R_{U'}, R_{U''}$ also overlap, so there is a valid choice $r = \psi(u)$.
  Now, we thicken all sets $U \in \U$ by a small enough $\epsilon$; it can be shown that if the \emph{thickened} sets overlap at $u$, then $U,U',U''$ themselves overlap, so again $R_U, R_{U'}, R_{U''}$ overlap and there is a valid chioce $r = \psi(u)$.

  \emph{Calibrated:} By construction of the thickened link, if $u$ maps to a wrong report, i.e. $\psi(u) \not\in \gamma(p)$, then $u$ must have at least distance $\epsilon$ to the optimal set $U$.
  We then show that the minimal gradient of the expected loss along any direction away from $U$ is lower-bounded, giving a constant excess expected loss at $u$.
\end{proof}
While we sketch the intuition here, the full proof is given in Section~\ref{app:calibration} of the Appendix.

@@

\begin{itemize}
\item The story we discussed: YK show $L_2$ is inconsistent.  Our framework lets us ask: with what discrete loss \emph{is} $L_2$ consistent?  (It also assures us that $L_2$ is consistent for something...) \jessie{Fixed}
\item The next part of the story: oh look, $L_2$ embeds something which is $\elltopk$ plus some other term, so (a) we can see very clearly what $L_2$ ``is doing'', and (b) we can see where to look for distributions yielding inconsistency, namely ones for which we actually prefer to report a set with $|r|<k$. \jessie{Fixed with question}
\end{itemize}

@@

Surrogates for this problem commonly take reports $u\in\reals^n$, with the link $\psi(u)$ mapping $u$ to the set of indices for the largest $k$ elements of $u$, with ties broken arbitrarily.
\citet{lapin2015top, lapin2016loss, lapin2018analysis} provide the following convex surrogate loss for this problem, which \citet{yang2018consistency} show to be inconsistent:%
\footnote{Yang and Koyejo also introduce a consistent surrogate, but it is non-convex.}
\begin{align}\label{eq:L-2-surrogate}
  L'(u)_y := \left( \frac{1}{k} \sum_{i=1}^k (u + \ones - e_y)_{[i]} - u_y \right)_+~,
\end{align}
where $e_y$ is $1$ in compnonent $y$ and 0 elsewhere, and $x_{[i]}$ is the $i^{th}$ largest component of $x$.

@@

We conclude with examples of how the embedding framework presented can be applied to understand surrogates given in the literature, including those for the abstain loss, top-$k$ loss, and Lov\'asz Hinge.
We use our link construction to understand calibrated links for abstain different than the one given by~\citet{ramaswamy2018consistent}.
While one top-$k$ surrogate has already been shown to be inconsistent, we show the similar discrete loss that the surrogate embeds.
Finally, we examine when \jessie{How to concisely explain what we do for Lov\'asz?}

>>>>

We augment this literature by studying a particularly natural approach for finding convex surrogates, wherein one ``embeds'' a discrete loss.
Specifically, we say a convex surrogate $L$ embeds a discrete loss $\ell$ if there is an injective embedding from the discrete reports (predictions) to a vector space such that (i) the original loss values are recovered, and (ii) a report is $\ell$-optimal if and only if the embedded report is $L$-optimal.
If this embedding can be extended to a calibrated link function, which maps approximately $L$-optimal reports to $\ell$-optimal reports, consistency follows~\cite{agarwal2015consistent}.
Common examples which follow this general construction include hinge loss as a surrogate for 0-1 loss and the abstain surrogate mentioned above.

@@

\begin{proof}[Sketch]
  (See Appendix~\ref{app:calibration} for the full proof.)
  \emph{Well-defined:}
  For the initial construction above, we argued that if some collection such as $U,U',U''$ overlap at a $u$, then their report sets $R_U, R_{U'}, R_{U''}$ also overlap, so there is a valid choice $r = \psi(u)$.
  Now, we thicken all sets $U \in \U$ by a small enough $\epsilon$; it can be shown that if the \emph{thickened} sets overlap at $u$, then $U,U',U''$ themselves overlap, so again $R_U, R_{U'}, R_{U''}$ overlap and there is a valid chioce $r = \psi(u)$.

  \emph{Calibrated:} By construction of the thickened link, if $u$ maps to a wrong report, i.e. $\psi(u) \not\in \gamma(p)$, then $u$ must have at least distance $\epsilon$ to the optimal set $U$.
  We then show that the minimal gradient of the expected loss along any direction away from $U$ is lower-bounded, giving a constant excess expected loss at $u$.
\end{proof}

@@

\btw{The story we discussed: YK show $L_2$ is inconsistent.  Our framework lets us ask: with what discrete loss \emph{is} $L_2$ consistent?  (It also assures us that $L_2$ is consistent for something...) Oh look, $L_2$ embeds something which is $\elltopk$ plus some other term, so (a) we can see very clearly what $L_2$ ``is doing'', and (b) we can see where to look for distributions yielding inconsistency, namely ones for which we actually prefer to report a set with $|r|<k$.}

@@

Surrogates for this problem commonly take reports $u\in\reals^n$, with the link $\psi(u) = \{u_{[1]},\ldots,u_{[k]}\}$, where $x_{[u]}$ is the $i^{th}$ largest component of $u$, with ties broken arbitrarily.
\citet{lapin2015top, lapin2016loss, lapin2018analysis} provide the following convex surrogate loss for this problem, which \citet{yang2018consistency} show to be inconsistent:%
\footnote{Yang and Koyejo also introduce a consistent surrogate, but it is non-convex.}
\begin{align}\label{eq:L-2-surrogate}
  L'(u)_y := \left( \frac{1}{k} \sum_{i=1}^k (u + \ones - e_y)_{[i]} - u_y \right)_+~,
\end{align}
where $e_y$ is $1$ in compnonent $y$ and 0 elsewhere.

@@

We conclude with examples of how the embedding framework presented can be applied to understand surrogates given in the literature, including those for the abstain loss, top-$k$ loss, and Lov\'asz Hinge.
We use our link construction to understand calibrated links for abstain different than the one given by~\citet{ramaswamy2018consistent}.
While one top-$k$ surrogate has already been shown to be inconsistent, we show the similar discrete loss that the surrogate embeds.
Finally, we use our framework to prove the inconsistency of the Lov\'asz Hinge.
